---
title: '`entrez_fetch` returns multiple records from the `nuccore` database when given one ID'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Thanks for making this package!  It's a huge help.  After a lot of successful use, I'm finding some very strange behavior.  Basically when I try to fetch nucliotide data for one ID I'm getting many records back.  Here's an example:

```{r, cache=TRUE}
# get record 
raw <- rentrez::entrez_fetch(db = 'nuccore', id = '403062956',
                             rettype = 'native', retmode = 'xml',
                             parsed = TRUE)

# transform into a named vector (XML structure preserved in the names...
# there's probably a much better way to do this)
rawList <- unlist(XML::xmlToList(raw))
```

The ID should produce a result for the species *Drosophila murphyi*. But the query in fact produces many records, most of which are not for *Drosophila murphyi*:

```{r}
# find all the times a species name is mentioned
allTax <- rawList[grep('Org-ref_taxname', names(rawList))]
names(allTax) <- NULL

# there are a lot of times
length(allTax)

# most are not for the expected species
sum(allTax == 'Drosophila murphyi')
```

If I ask for the FASTA file it behaves as expected and gives me one record for the right species:
```{r}
rawFASTA <- rentrez::entrez_fetch(db = 'nuccore', id = '403062956',
                             rettype = 'fasta')
cat(rawFASTA)
```
